### 2018-04-15 experiments.tex
ok

We introduced a subtle bug into {\tt pyfakefs}, where the {\tt remove}
call checks that its target is not a directory, and returns the
correct error, but still carries out the remove operation.  Using {\tt
  os.remove} to delete directories does not break any file system
invariants, but violates the Python {\tt os} specification (and,
indirectly, the usual POSIX implementation behavior where {\tt unlink}
does not work for directories).  Detecting this bug using the TSTL
{\tt pyfakefs} harness is normally impossible without using another
file system as a reference.  However, the fault was detected
immediately, even without using a reference, when we compiled the harness
with the {\tt --checkFailureDeterminism} flag.  Because vertical
reduction does not require running complete tests multiple times, and
does not affect the delta-debugging algorithm's performance, reducing
the failing test to 3 steps required less than a second.
Moreover, the overhead for adding a check for failure determinism was
less than 8\%.

>>>>

We introduced a subtle bug into {\tt pyfakefs}, where the {\tt remove}
call checks that its target is not a directory, and returns the
correct error, but still carries out the remove operation.  Using {\tt
  os.remove} to delete directories does not break any file system
invariants, but violates the Python {\tt os} specification (and,
indirectly, the usual POSIX implementation behavior where {\tt unlink}
does not work for directories).  Detecting this bug using the TSTL
{\tt pyfakefs} harness is normally impossible without using another
file system as a reference.  However, the fault was detected
immediately, even without using a reference, when we compiled the harness
with the {\tt --checkFailureDeterminism} flag.  Because vertical
reduction does not require running complete tests multiple times, and
does not affect the delta-debugging algorithm's performance, reducing
the failing test to 3 steps required less than a second.
Moreover, the overhead for the check for failure determinism in a
version of the code without the {\tt remove} error was
less than 8\%.  Detecting the fault using a reference file system also
required 17\% more time, and took about twice as long to reduce to a
slightly longer failing test, which did not have {\tt remove} as its
final operation (since further file system interaction is required to
expose the bad state).
